Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Só falta o Jaccard
Final (falta Gabriel)

\begin{block}{Basicly:}

@@

\begin{block}{Uniquesses of partial and complete libraries using Jaccard index}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.3]{Libraries_unique}
\caption{Uniquesses of partial and complete libraries using Jaccard index}.
\label{fig:Libraries_unique}
\end{figure}

@@

@@

%%%%% Thanks page
\begin{frame}
\frametitle{Thanks}
\vskip20pt

@@

\vskip20pt

@@

\vskip12pt
\end{center}

\titlepage
\end{frame}

>>>>

\begin{block}{Basically:}

@@

\begin{block}{Uniquesses of partial and complete libraries using Jaccard index $ J(A,B)=\left| \frac{A\cup B} {A\cap B} \right|$}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.25]{Libraries_unique}
\caption{Uniquesses of partial and complete libraries using Jaccard index}.
\label{fig:Libraries_unique}
\end{figure}

@@

\item[\checkmark]Criminal trafficking of CP on p2p networks is
widespread, with no easy answers for law enforcement looking
to curtail it.

\item[\checkmark]Triage as a strategy due:

	\item Diversity in peers’ location.
	\item Redundancy of the libraries.
	\item Many p2p networks.
	\item Limited law enforcement resources.

\item[\checkmark]Investigators should carefully choose peers
to investigate and remove from p2p networks.

\item[\checkmark]Naïve approaches to triage are ineffective and optimal approaches are NP-Hard.

\item[\checkmark]Tractable heuristics yield reasonable and useful results.

\item[\checkmark]Use of these heuristics are complemented by the
discovery of aggressive subgroups of CP traffickers.

\item[\checkmark]No significant evidence of users attempting to hide file libraries.

	\item Libraries are largely unique, strongly implying a unique user behind each such library.

\item[\checkmark]Some users do use Tor, but most do so inconsistently.

It is an open question as to whether network-observable
behaviors correlate with off-line behaviors, such as
child molestation.

@@

%%%%% Thanks page
\section{Thanks}
\begin{frame}
\frametitle{Thanks}
\vskip30pt

@@

\vskip30pt

@@

\vskip12pt

Adriano R. Ruggero, Gabriel Rodrigues, Mário F. Brito, Maurício L. Perez

\end{center}

%%\titlepage
\end{frame}
